Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

%=================================
%Yufei's stuff
%\usepackage{amsmath}
\usepackage{balance}
%\usepackage{times}
\usepackage{microtype}

@@

\extraspacing {\bf Set $\bm{H'}$.} Take any horizontal segment $h = [x_1, x_2] \times y \in H$. Let $p$ be the rightmost point on $h$ satisfying the condition that at least one left-end covering rectangle of $h$ in $R_{k-2}$ covers $p$. This $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we refer to the segment $h' = [x_1, x] \times y$ as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.

>>>>

%test
%=================================
%Yufei's stuff
%\usepackage{amsmath}
\usepackage{balance}
%\usepackage{times}
\usepackage{microtype}

@@

\extraspacing {\bf Set $\bm{H'}$.} Take any horizontal segment $h = [x_1, x_2] \times y \in H$. Recall from Section~\ref{sec:bricks} that a left-end covering rectangle of $h$ is a rectangle covering the left endpoint of $h$. 
Let $p$ be the rightmost point on $h$ such that at least one left-end covering rectangle of $h$ in $R_{k-2}$ covers $p$. This $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we refer to the segment $h' = [x_1, x] \times y$ as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.
